Tensor anisotropy as a tracer of cosmic voids

### 2015-03-18 cosmic_voids.tex
adding text to captions

@@

  \captionof{figure}{\small Overdensity (left) and Fractional
    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
    over all grid cells in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include
    $50\%$ of the cells in each bin.
    This information is necesary to define void boundaries in
    the watershed algorithm. 
    The vertical lines show the equivalent threshold values for the
    T-Web and V-web in order to have voids composed by cells with
    Fractional Anisotrop equal or less than $0.95$.}
  \label{fig:L1_correlations}

@@

  \captionof{figure}{\small Left panel, void size distribution. Right
    panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
    function of the effective radius. The continous (dashed)
    curves correspond to the T-Web (V-Web).}
  \label{fig:volume_function}

>>>>

  \captionof{figure}{\small Overdensity (left) and Fractional
    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
    over all grid cells in the Bolshoi simulation. 
    Thick central lines are the median and filled regions include
    $50\%$ of the cells in each bin.
    This information is necesary to define void boundaries in
    the watershed algorithm. 
    The vertical lines show the equivalent threshold values for the
    T-Web and V-web in order to have voids composed by cells with
    Fractional Anisotrop equal or less than $0.95$. 
   This threshold on the eigenvalues does not influence our
   computations. 
   We show it as a guide to readers familiar with the
   order of magnitude expectation for this threshold.}
  \label{fig:L1_correlations}

@@

@@

  \captionof{figure}{\small Left panel, void size distribution. Right
    panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
    function of the effective radius. The continous (dashed)
    curves correspond to the T-Web (V-Web).
    The abundance for small ($r_{eff}<2.0\hMpc$) overcompensated voids
    shoots up in the V-Web scheme.
    We provide in the body of the paper two reasons for this behaviour.}
  \label{fig:volume_function}
